Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-21 article.tex
Comment + make 3-2 rows

\begin{figure}
\centering
\subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}\\
\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}
\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}\\

\subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.}
\label{fig:filtered-signal}
\end{figure}

>>>>

\begin{figure}
\centering
\subfigure[Original]{\includegraphics[width=0.3\textwidth]{images/original_curve.pdf} \label{fig:original_curve}}
\subfigure[Low-pass $f_1(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/filter_curve.pdf} \label{fig:lp_curve}}
\subfigure[High-pass $g(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/diff_curve.pdf} \label{fig:hp_curve}}\\
\subfigure[Thresholding $h(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/threshold_curve.pdf} \label{fig:threshold_curve}}
\subfigure[Weights $w(x_i^t)$]{\includegraphics[width=0.3\textwidth]{images/weights_curve.pdf} \label{fig:original_curve}}
\caption{Signal processing process for extracting peaks from the raw fluorescence data.
         \textcolor{red}{AJ: The bottom axe is hidden on some figures.}}
\label{fig:filtered-signal}
\end{figure}
